\doublespacing
\begin{center}
\textbf{\Large Stanford University}

\textbf{\Large Department of Electrical Engineering}

\Large EE 264: Digital Signal Processing 

\Large Final Exam

\Large Summer, 2018
\end{center}
\vspace{-0.5cm}
\rule{\textwidth}{1pt}

\noindent\textbf{Name:} \rule{0.4\textwidth}{0.5pt} \qquad  \textbf{Date and time:} \rule{0.3\textwidth}{0.5pt}

\noindent\textbf{SUNet ID:} \rule{0.3\textwidth}{0.5pt}\qquad 
\textbf{SCPD Student?} yes no

\mbox{}\\
\textbf{Instructions:}
\singlespacing
\begin{enumerate}
\item This is a 24h-take home exam. 
\item Carefully read over and understand the exam problems before you start.
\item The exam is open book and open notes. You may use all available references.
\item Be clear, organized, and concise in your answers.
\item During grading we will not propagate errors. We will evaluate your answers to each question independently from previous answers.
\item Please submit your solutions in a single .pdf file on Gradescope. Your solutions \underline{must} include derivations, clearly labeled plots, and code you developed. Your submission \underline{must} also include this cover page signed. 
\item Do \underline{not} communicate with others about the exam even after you have taken it, as some students will take the exam at a different time.
\item Do \underline{not} post questions on Piazza during the exam. If you have questions, please contact the teaching staff \{anchit, jkperin\}@stanford.edu. However, we will not provided additional hints or check your answers.
\end{enumerate}

\noindent\textbf{The Stanford University Honor Code:}
\begin{quote}
I attest that I have not given or received aid in this examination, and that I have done my share and taken an active part in seeing to it that others as well as myself uphold the spirit and letter of the Honor Code.
\end{quote}
\vspace{1mm}

\begin{center}\textbf{Signature:} \rule{0.7\textwidth}{0.5pt}\end{center}

\doublespacing
\vspace{0.1cm}
\begin{center}
\begin{tabular}{ccc}
\textbf{Problem} & \textbf{Points} & \textbf{Score} \\
1 & 60 & \\
2 & 60 & \\
\end{tabular}
\end{center}
\singlespacing