\doublespacing
\begin{center}
\textbf{\Large Stanford University}

\textbf{\Large Department of Electrical Engineering}

\Large EE 264: Digital Signal Processing 

\Large Midterm Exam

\Large August 1st, 2017
\end{center}
\vspace{-0.5cm}
\rule{\textwidth}{1pt}

\noindent\textbf{Name:} \rule{0.85\textwidth}{0.5pt}

\noindent\textbf{SUNet ID:} \rule{0.3\textwidth}{0.5pt}\qquad 
\textbf{SCPD Student?} yes no

\mbox{}\\
\textbf{Instructions:}
\singlespacing
\begin{enumerate}
\item The exam duration is \textbf{110 minutes}.
\item Carefully read over and understand the exam problem before you start. \textit{Solutions do not require lengthy calculations or derivations.}
\item The exam is open book and open notes. You may also use a computer.
\item Do all work in the space provided. If you need more room, use the back of the previous page, but be sure to indicate that you have done that.
\item Be clear, organized, and concise in your answers.
\item SCPD students may start the exam at any time on Tuesday, August 1st. However, they must have an University-approved proctor and respect the exam duration.
\item Do \underline{not} communicate with others about the exam even after you have taken it, as some students will take the exam at a different time.
\end{enumerate}

\noindent\textbf{The Stanford University Honor Code:}
\begin{quote}
I attest that I have not given or received aid in this examination, and that I have done my share and taken an active part in seeing to it that others as well as myself uphold the spirit and letter of the Honor Code.
\end{quote}
\vspace{1mm}

\begin{center}\textbf{Signature:} \rule{0.7\textwidth}{0.5pt}\end{center}

\doublespacing
\vspace{0.1cm}
\begin{center}
\begin{tabular}{ccc}
\textbf{Problem} & \textbf{Points} & \textbf{Score} \\
1 & 30 & \\
2 & 30 & \\
3 & 20 & \\
4 & 20 & \\
TOTAL & 100 & \\
\end{tabular}
\end{center}
\singlespacing